Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-27 analysis/paper/paper.Rmd
comment code chunk

install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

invisible(lapply(packages,
                 library,
                 character.only = TRUE))

>>>>

# install packages if needed
install.packages(setdiff(packages,
                         rownames(installed.packages())),
                 repos = "http://cran.us.r-project.org",
                 dependencies = TRUE)

# load packages for use in knitting Rmd
invisible(lapply(packages,
                 library,
                 character.only = TRUE))
